\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-07-13 paper/paper.tex
small edit

\section{Background}
\label{sec:Background}
In engineering applications, a product can often fail from one out of a set of possible malfunctioning components.  For example, a computer system can break if the mother board, disc drive or power supply stop working.  Circuit boards (CB) can fail due to a manufacturing defect or later as a result of wearout.  The general name for such products is a series system where the lifetime of the product is the minimum failure time across $s$ different components or risks \cite{nelson}.  A common assumption in series systems is the time to failure for each risk, $s$, is statistically independent.  Thus, the overall reliability of a unit is modeled using the product rule across all $s$ risks.  Parameter estimation is straightforward if the cause of failure is known for each observation.  With engineering systems data, however, the exact cause of failure is frequently unknown or masked from the analyst.  \\

>>>>

\section{Background}
\label{sec:Background}
In engineering applications, a product can often fail from one out of a set of possible malfunctioning components.  For example, a computer system can break if the mother board, disc drive or power supply stop working.  Circuit boards (CB) can fail due to a manufacturing defect or later as a result of wearout.  The general name for such products is a series system where the lifetime of the product is the minimum failure time across different components or risks \cite{nelson}.  A common assumption in series systems is the time to failure for each risk is statistically independent.  Thus, the overall reliability of a unit is modeled using the product rule across all risks.  Parameter estimation is straightforward if the cause of failure is known for each observation.  However, in many situations the cause of failure is unknown to the analyst. This is referred to in the literature as "masking".\\
